Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-23 ms.tex
words for planet properties

In \paperit, we present only parameters directly observable from the \KT\
light curve itself: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.

For each candidate, we fit a transit and systematic model simultaneously
to the data.
The transit model is an exposure-time integrated, two-parameter limb darkened 
light curve \citep{Mandel02,Kipping10b}.
We parameterize... \dfmtodo{What are the parameters in the model?}

This method enable us to marginalize over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

The results are given in Table 3.

\dfmtodo{Add more to this section.}

@@

One system, EPIC 201828749, is known to be a binary through AO imaging
as discussed in \textsection\ref{sec:AO}. 
In this case, we do account for the dilution induced by the companion. 
From our relative $JHK$ photometry of the two stars, we infer an expected flux
ratio between the two stars in the \kep\ bandpass, inflating the transit depth by 
this factor to account for the dilution. 
We marginalize  \dfmtodo{More text...}

>>>>

In \paperit, only parameters directly observable from the \KT\ light curve
itself were reported: the period, time of transit center, and transit depth.
With stellar properties now in hand, we can convert these observational
results into fundamental parameters of each planet candidate.
For each candidate, we fit the light curve using a physical transit model
\citep{Mandel02, Kipping10b} simultaneously with the systematics model
described by \paperit.
We use \texttt{emcee} to sample from the posterior probability distribution
for the stellar---limb darkening coefficients, mass, radius, and effective
temperature---and planetary---radius, period, phase, impact parameter,
eccentricity, and argument of periapsis---parameters, conditioned on the
light curve and the measured stellar properties.
Following \paperit, the likelihood function that we use is marginalized over
the parameters of the systematics model.
To incorporate the stellar measurements, we approximate the measurements as a
three-dimensional Gaussian in mass, radius, and effective temperature.

@@

The planet parameters measured by this analysis are listed in Table 3.

%%%
%%%  I haven't actually done this... perhaps I can do it in response to
%%%  referee if they ask for it...
%%%
% One system, EPIC 201828749, is known to be a binary through AO imaging
% as discussed in \textsection\ref{sec:AO}.
% In this case, we do account for the dilution induced by the companion.
% From our relative $JHK$ photometry of the two stars, we infer an expected flux
% ratio between the two stars in the \kep\ bandpass, inflating the transit depth
% by this factor to account for the dilution.
% We marginalize  \dfmtodo{More text...}
